Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-03 Experiments.tex
Comment section 5 addressed, ORTE citations added
Added references to Section 5.3 Figures in the appendix
Minor fix

\subsection{Experiments}

@@

\begin{figure}[!htb]
        \includegraphics[height=4.5cm,width=\columnwidth]{./figures/NGE/weak1.pdf}
    \caption{Weak scalability: average pilot duration, average  duration of a
    single AthenaMP execution, and pilot's overhead as a function of different pilot sizes. \jhanote{Caption should be in consistent order as the bars in the figure. Ideally pilot first then AthenMP.}}
\label{fig:weakScal1a}
\end{figure}

>>>>

\subsection{Experiments}\label{sec:ngeExp}

@@

\begin{figure}[!htb]
        \includegraphics[height=4.5cm,width=\columnwidth]{./figures/NGE/weak1.pdf}
    \caption{Weak scalability: average pilot duration, average  duration of a
    single AthenaMP execution, and pilot's overhead as a function of different pilot sizes (200, 500, 1000 and 2000 nodes). \jhanote{Caption should be in consistent order as the bars in the figure. Ideally pilot first then AthenMP.}\aanote{DONE}}
\label{fig:weakScal1a}
\end{figure}
